% template created by: Russell Haering. arr. Joseph Crop
\documentclass[12pt,letterpaper]{article}
\usepackage{anysize}
\usepackage{graphicx}
\usepackage{enumerate}
\marginsize{2cm}{2cm}{1cm}{1cm}


\usepackage{listings}
\usepackage{amsmath}
\usepackage{nicefrac}


\begin{document}

\begin{titlepage}
    \vspace*{4cm}
    \begin{flushright}
    {\huge
        ECE 375 Pre-Lab 7\\[1cm]
    }
    {\large
     	 Timer/Counters
    }
    \end{flushright}
    \begin{flushleft}
    Lab Time: Thursday 10:00 - 11:50
    \end{flushleft}
    \begin{flushright}
    Jeremy Fischer
    
    \vfill
    \rule{5in}{.5mm}\\
    TA Signature
    \end{flushright}

\end{titlepage}


\section{Pre-Lab}

	\begin{enumerate}
		\item
		 List the correct sequence of AVR assembly instructions needed to store the contents of registers R25:R24 into Timer/Counter1’s 16-bit register, TCNT1. 
		 (You may assume that registers R25:R24 have already been initialized to contain some 16-bit value.)
		
		\begin{verbatim}
			OUT TCNT1L, R24
			OUT TCNT1H, R25
		\end{verbatim}
		
		
		
		
		
		\item
		 List the correct sequence of AVR assembly instructions needed to load the contents of Timer/Counter1’s 16-bit register, TCNT1, into registers R25:R24.
		
		
		\begin{verbatim}
			IN R24, LOW(TCNT1)	
			IN R25, HIGH(TCNT1)
		\end{verbatim}
		
		
		
		
		\item
		Suppose Timer/Counter0 (an 8-bit timer) has been configured to operate in Normal mode, and with no prescaling (i.e., clkT0 = clkI/O = 16 MHz). 
		The decimal value “128” has just been written into Timer/Counter0’s 8-bit register, TCNT0. 
		How long will it take for the TOV0 flag to become set? Give your answer as an amount of time, \textbf{not} as a number of cycles.
		
		
		$Delay = \dfrac{(MAX + 1 - value) * prescale} {clkI/O}$
		
		And clkI/O is the frequency which is $f = \frac{1}{T}$ where T is the period.
		So T = 62.5 nanoseconds, MAX = 256, value = 128, prescale = 1 because it is non-existant.
		Therefore,
		
		$Delay = (255 + 1 - 128) * 1 * 0.000000062.5 = $  8 microseconds.
	\end{enumerate}
\end{document}

